Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-02-15 text/paper2/ms.tex
typos

Although the \gaia\ project will deliver hundreds of millions of stars useful for dynamical inference,
  it still might be that the most relevant stellar samples for inferring the Milky Way potentail might be very small in the end.
One reason is that if distances turn out to be important, stars that produce good distance estimates might be much more
  valuable than typical stars in the sample.
At halo distances, \gaia's parallaxes are not expected to be better than the distance indicators produced by the best
  variable stars observed at the best wavelengths; for example, near-infrared observations of RR Lyrae stars
  can in principle deliver XX percent photometric distances at essentially all halo distances (CITATIONS).
These valuable stars are rare (and age and metallicity dependent);
  there could be many cold structures in the Milky Way halo that are highly constraining
  on the potential in principle, but which contain only a few good distance-indicating members.
That said, it is not yet known what the trade-offs are between having many stars at low precision and a few at high precision,
  nor is it known how valuable distance information really is, when a structure contains many precisely observed members.

>>>>

Although the \gaia\ project will deliver hundreds of millions of stars useful for dynamical inference,
  it still might be that the most relevant stellar samples for inferring the Milky Way potential might be very small in the end.
One reason is that if distances turn out to be important, stars that produce good distance estimates might be much more
  valuable than typical stars in the sample.
At halo distances, \gaia's parallaxes are not expected to be better than the distance indicators produced by the best
  variable stars observed at the best wavelengths; for example, near-infrared observations of RR Lyrae stars
  can in principle deliver XX percent photometric distances at essentially all halo distances (CITATIONS).
These valuable stars are rare (and their abundances are age and metallicity dependent);
  there could be many cold structures in the Milky Way halo that are highly constraining
  on the potential in principle, but which contain only a few good distance-indicating members.
That said, it is not yet known what the trade-offs are between having many stars at low precision and a few at high precision,
  nor is it known how valuable distance information really is, when a structure contains many precisely observed members.
